Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-10-19 paper/main.tex
table

%: LOP syntéticas, todas en una gráfica. 
\begin{figure}
  \centering%
  \includegraphics[width=\textwidth]{img/synthetic_LOP_combined}
  \caption{Mean fitness  (and standard deviation)  of each solution evaluated by each algorithm on LOP synthetic instances.\label{fig:lop_synth}}
\end{figure}

@@

  \resizebox{\textwidth}{!}{
\begin{tabular}{lllllrrr}

@@

Problem &       Instance &           UMM fitness &           CEGO fitness &     Confidence interval &  UMM Runtime &  CEGO Runtime &  CEGO F. evaluations \\
\midrule
    LOP &    N-t1d100.01 &       76119.6 (915.4) &        78696.6 (811.4) &        (1763.5, 3390.5) &          3.2 &          72.5 &                111.8 \\
    LOP &    N-t1d100.02 &       76827.7 (891.0) &        79686.5 (367.9) &        (2194.5, 3523.1) &          3.2 &          72.9 &                110.7 \\
    LOP &    N-t1d150.01 &     179508.3 (1647.9) &      187605.5 (1906.9) &        (6420.3, 9774.1) &          6.5 &          72.7 &                 73.9 \\
    LOP &    N-t1d150.02 &     177592.8 (1196.2) &       184320.9 (973.5) &        (5700.5, 7755.7) &          6.5 &          73.2 &                 74.1 \\
    LOP &    N-t1d200.01 &     323513.6 (1371.2) &      335391.1 (2289.0) &      (10076.1, 13678.9) &         10.7 &          73.2 &                 55.6 \\
    LOP &    N-t1d200.02 &     319675.8 (2242.6) &      333149.5 (2497.2) &      (11242.0, 15705.4) &         10.6 &          73.7 &                 56.5 \\
    LOP &    N-t2d150.01 &       15297.7 (563.5) &        24682.7 (976.6) &       (8622.2, 10147.8) &          7.0 &          72.9 &                 74.6 \\
    LOP &    N-t2d150.02 &       14724.9 (667.5) &       24250.8 (1354.9) &       (8495.1, 10556.7) &          7.1 &          72.8 &                 74.8 \\
    LOP &    N-t2d200.01 &      33465.2 (2001.0) &       57098.6 (4452.8) &      (20284.5, 26982.3) &         11.2 &          73.3 &                 56.3 \\
    LOP &    N-t2d200.02 &      35901.8 (2077.5) &       54895.6 (4589.7) &      (15539.1, 22448.5) &         11.2 &          73.5 &                 55.6 \\
    LOP &       N-p50-01 &       21027.6 (711.8) &        21431.2 (299.5) &         (-128.1, 935.3) &          0.9 &          72.3 &                219.9 \\
    LOP &       N-p50-02 &       21613.6 (596.4) &        22021.1 (275.6) &          (-42.5, 857.5) &          0.9 &          72.3 &                217.3 \\
    LOP &       N-atp111 &          594.0 (15.4) &           693.1 (10.3) &           (86.7, 111.5) &          4.1 &          72.5 &                 98.7 \\
    LOP &       N-atp134 &          756.3 (21.3) &           880.5 (18.6) &          (105.4, 143.0) &          5.7 &          72.8 &                 83.0 \\
    LOP &  N-be75eec\_150 &   1415208.5 (58593.5) &    1666193.1 (72310.8) &    (188960.6, 313008.6) &          6.9 &          72.9 &                 74.0 \\
    LOP &  N-be75eec\_250 &  4431271.0 (109756.7) &   5214413.0 (166701.4) &    (649040.8, 917243.2) &         15.5 &          73.7 &                 44.9 \\
    LOP &   N-be75np\_150 &   3204878.3 (80704.1) &    3742444.0 (88500.2) &    (457944.2, 617187.2) &          6.9 &          72.9 &                 74.2 \\
    LOP &   N-be75np\_250 &  9544754.9 (260523.9) &  10887427.8 (159642.5) &  (1136635.8, 1548710.0) &         15.5 &          74.0 &                 45.3 \\
   PFSP &      rec05.txt &         1330.7 (17.9) &          1317.9 (25.1) &            (-33.4, 7.8) &          0.1 &          38.9 &                400.0 \\
   PFSP &      rec13.txt &         2158.7 (29.5) &          2128.2 (25.0) &           (-56.2, -4.8) &          0.1 &          38.9 &                400.0 \\
   PFSP &      rec19.txt &         2405.1 (12.6) &          2398.6 (19.8) &            (-22.3, 9.3) &          0.3 &          82.1 &                400.0 \\
    QAP &      kra32.dat &     116320.0 (4673.5) &      115907.0 (4663.4) &       (-4799.3, 3973.3) &          0.3 &          95.8 &                400.0 \\
    QAP &      nug12.dat &          660.4 (17.3) &           624.2 (26.3) &          (-57.3, -15.1) &          0.0 &          14.8 &                400.0 \\
    QAP &      nug30.dat &         7474.0 (83.9) &          7486.8 (40.4) &           (-50.8, 76.4) &          0.3 &          84.3 &                400.0 \\
    QAP &      tho30.dat &     191482.0 (4419.7) &      192416.0 (2584.2) &       (-2527.0, 4395.0) &          0.3 &          85.1 &                400.0 \\

@@

>>>>

%: LOP syntéticas, todas en una gráfica. 
\begin{figure}[tb]
  \centering%
  \includegraphics[width=\textwidth]{img/synthetic_LOP_combined}
  \caption{Mean fitness  (and standard deviation)  of each solution evaluated by each algorithm on LOP synthetic instances.\label{fig:lop_synth}}
\end{figure}

@@

   \newcommand{\mcolc}[2]{\multicolumn{#1}{c}{\bf #2}}
\begin{table}
 \caption{Results.\label{tab:results}}
 \resizebox{\textwidth}{!}{%
\begin{tabular}{*{6}{r}rl*{3}{r}}

@@

           &                  & \mcolc{4}{Mean fitness (sd)} &  \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI for the\\mean difference}}}         & \mcolc{2}{Mean runtime}             & \bf \multirow[b]{2.45}{*}{\shortstack{Mean FE\\CEGO}}\\\cmidrule{3-6}\cmidrule(lr){9-10}
\bf Problem & \bf     Instance & \mcolc{2}{UMM}               & \mcolc{2}{CEGO} & & & \bf UMM  & \bf CEGO                                  & \bf            \\\midrule
    LOP &    N-t1d100.01 &       76119.6&(915.4) &        78696.6&(811.4) &       $[$1763.5,&3390.5$]$ &          3.2 &          72.5 &                111.8 \\
    LOP &    N-t1d100.02 &       76827.7&(891.0) &        79686.5&(367.9) &       $[$2194.5,&3523.1$]$ &          3.2 &          72.9 &                110.7 \\
    LOP &    N-t1d150.01 &     179508.3&(1647.9) &      187605.5&(1906.9) &       $[$6420.3,&9774.1$]$ &          6.5 &          72.7 &                 73.9 \\
    LOP &    N-t1d150.02 &     177592.8&(1196.2) &       184320.9&(973.5) &       $[$5700.5,&7755.7$]$ &          6.5 &          73.2 &                 74.1 \\
    LOP &    N-t1d200.01 &     323513.6&(1371.2) &      335391.1&(2289.0) &     $[$10076.1,&13678.9$]$ &         10.7 &          73.2 &                 55.6 \\
    LOP &    N-t1d200.02 &     319675.8&(2242.6) &      333149.5&(2497.2) &     $[$11242.0,&15705.4$]$ &         10.6 &          73.7 &                 56.5 \\
    LOP &    N-t2d150.01 &       15297.7&(563.5) &        24682.7&(976.6) &      $[$8622.2,&10147.8$]$ &          7.0 &          72.9 &                 74.6 \\
    LOP &    N-t2d150.02 &       14724.9&(667.5) &       24250.8&(1354.9) &      $[$8495.1,&10556.7$]$ &          7.1 &          72.8 &                 74.8 \\
    LOP &    N-t2d200.01 &      33465.2&(2001.0) &       57098.6&(4452.8) &     $[$20284.5,&26982.3$]$ &         11.2 &          73.3 &                 56.3 \\
    LOP &    N-t2d200.02 &      35901.8&(2077.5) &       54895.6&(4589.7) &     $[$15539.1,&22448.5$]$ &         11.2 &          73.5 &                 55.6 \\
    LOP &       N-p50-01 &       21027.6&(711.8) &        21431.2&(299.5) &        $[$-128.1,&935.3$]$ &          0.9 &          72.3 &                219.9 \\
    LOP &       N-p50-02 &       21613.6&(596.4) &        22021.1&(275.6) &         $[$-42.5,&857.5$]$ &          0.9 &          72.3 &                217.3 \\
    LOP &       N-atp111 &          594.0&(15.4) &           693.1&(10.3) &          $[$86.7,&111.5$]$ &          4.1 &          72.5 &                 98.7 \\
    LOP &       N-atp134 &          756.3&(21.3) &           880.5&(18.6) &         $[$105.4,&143.0$]$ &          5.7 &          72.8 &                 83.0 \\
    LOP &  N-be75eec\_150 &   1415208.5&(58593.5) &    1666193.1&(72310.8) &   $[$188960.6,&313008.6$]$ &          6.9 &          72.9 &                 74.0 \\
    LOP &  N-be75eec\_250 &  4431271.0&(109756.7) &   5214413.0&(166701.4) &   $[$649040.8,&917243.2$]$ &         15.5 &          73.7 &                 44.9 \\
    LOP &   N-be75np\_150 &   3204878.3&(80704.1) &    3742444.0&(88500.2) &   $[$457944.2,&617187.2$]$ &          6.9 &          72.9 &                 74.2 \\
    LOP &   N-be75np\_250 &  9544754.9&(260523.9) &  10887427.8&(159642.5) & $[$1136635.8,&1548710.0$]$ &         15.5 &          74.0 &                 45.3 \\
   PFSP &      rec05.txt &         1330.7&(17.9) &          1317.9&(25.1) &           $[$-33.4,&7.8$]$ &          0.1 &          38.9 &                400.0 \\
   PFSP &      rec13.txt &         2158.7&(29.5) &          2128.2&(25.0) &          $[$-56.2,&-4.8$]$ &          0.1 &          38.9 &                400.0 \\
   PFSP &      rec19.txt &         2405.1&(12.6) &          2398.6&(19.8) &           $[$-22.3,&9.3$]$ &          0.3 &          82.1 &                400.0 \\
    QAP &      kra32.dat &     116320.0&(4673.5) &      115907.0&(4663.4) &      $[$-4799.3,&3973.3$]$ &          0.3 &          95.8 &                400.0 \\
    QAP &      nug12.dat &          660.4&(17.3) &           624.2&(26.3) &         $[$-57.3,&-15.1$]$ &          0.0 &          14.8 &                400.0 \\
    QAP &      nug30.dat &         7474.0&(83.9) &          7486.8&(40.4) &          $[$-50.8,&76.4$]$ &          0.3 &          84.3 &                400.0 \\
    QAP &      tho30.dat &     191482.0&(4419.7) &      192416.0&(2584.2) &      $[$-2527.0,&4395.0$]$ &          0.3 &          85.1 &                400.0 \\

@@

\end{table}
